NFC and burnout in teachers - A replication and extension study

### 2021-09-09 Manuscript/Manuscript.Rmd
added years spent teaching to data frame

  score_data <- data.frame(id = c(1:180),
                           mbi = rep(0,180),
                           mbi_ee = rep(0,180), mbi_dp = rep(0,180), mbi_rpe = rep(0,180),
                           erq = rep(0,180),
                           erq_supp = rep(0,180), erq_reap = rep(0,180),
                           scs = rep(0,180),
                           ncs = rep(0,180),
                           nfc1 = rep(0,180), nfc2 = rep(0,180), nfc3 = rep(0,180), nfc4 = rep(0,180),
                           dth = rep(0,180),
                           dth1 = rep(0,180), dth2 = rep(0,180), dth3 = rep(0,180),
                           dtl = rep(0,180),
                           dtl1 = rep(0,180), dtl2 = rep(0,180), dtl3 = rep(0,180),
                           drf = rep(0,180),
                           drf1 = rep(0,180), drf2 = rep(0,180), drf3 = rep(0,180),
                           covb = rep(0,180))

@@

  for (i in 1:nrow(data)) {
    score_data[i,c(2:ncol(score_data))] <- c(rowSums(mbi[i,]),
                                             rowSums(mbi[i,keylist$mbi_ee]), rowSums(mbi[i,keylist$mbi_dp]), rowSums(mbi[i,keylist$mbi_rpe]),
                                             rowSums(erq[i,]),
                                             rowSums(erq[i,keylist$erq_supp]), rowSums(erq[i,keylist$erq_reap]),
                                             rowSums(scs[i,]),
                                             rowSums(ncs[i,]),
                                             rowSums(ncs[i,keylist$parcel1]), rowSums(ncs[i,keylist$parcel2]), rowSums(ncs[i,keylist$parcel3]), rowSums(ncs[i,keylist$parcel4]),
                                             rowSums(dth[i,]),
                                             dth[i,1], dth[i,2], dth[i,3],
                                             rowSums(dtl[i,]),
                                             dtl[i,1], dtl[i,2], dtl[i,3],
                                             rowSums(drf[i,]),
                                             drf[i,1], drf[i,2], drf[i,3],
                                             rowSums(covb[i,]))
  }

@@

  # Plot a big correlational matrix to check for non-linear associations and unexpected outliers
  multicorrplot <- ggpairs(score_data[,c(2,3,4,5,9,10,15,19,23,27)], lower = list(continuous = my_fn))

>>>>

  score_data <- data.frame(id = c(1:180),
                           years = data$yearsteaching,
                           mbi = rep(0,180),
                           mbi_ee = rep(0,180), mbi_dp = rep(0,180), mbi_rpe = rep(0,180),
                           erq = rep(0,180),
                           erq_supp = rep(0,180), erq_reap = rep(0,180),
                           scs = rep(0,180),
                           ncs = rep(0,180),
                           nfc1 = rep(0,180), nfc2 = rep(0,180), nfc3 = rep(0,180), nfc4 = rep(0,180),
                           dth = rep(0,180),
                           dth1 = rep(0,180), dth2 = rep(0,180), dth3 = rep(0,180),
                           dtl = rep(0,180),
                           dtl1 = rep(0,180), dtl2 = rep(0,180), dtl3 = rep(0,180),
                           drf = rep(0,180),
                           drf1 = rep(0,180), drf2 = rep(0,180), drf3 = rep(0,180),
                           covb = rep(0,180))

@@

  for (i in 1:nrow(data)) {
    score_data[i,c(3:ncol(score_data))] <- c(rowSums(mbi[i,]),
                                             rowSums(mbi[i,keylist$mbi_ee]), rowSums(mbi[i,keylist$mbi_dp]), rowSums(mbi[i,keylist$mbi_rpe]),
                                             rowSums(erq[i,]),
                                             rowSums(erq[i,keylist$erq_supp]), rowSums(erq[i,keylist$erq_reap]),
                                             rowSums(scs[i,]),
                                             rowSums(ncs[i,]),
                                             rowSums(ncs[i,keylist$parcel1]), rowSums(ncs[i,keylist$parcel2]), rowSums(ncs[i,keylist$parcel3]), rowSums(ncs[i,keylist$parcel4]),
                                             rowSums(dth[i,]),
                                             dth[i,1], dth[i,2], dth[i,3],
                                             rowSums(dtl[i,]),
                                             dtl[i,1], dtl[i,2], dtl[i,3],
                                             rowSums(drf[i,]),
                                             drf[i,1], drf[i,2], drf[i,3],
                                             rowSums(covb[i,]))
  }

@@

  # Plot a big correlational matrix to check for non-linear associations and unexpected outliers
  multicorrplot <- ggpairs(score_data[,c(2,3,4,5,6,10,11,16,20,24,28)], lower = list(continuous = my_fn))

  # It looked like there was an outlier in the data, especially visible in the MBI data
  # Check for the outlier in particular
